fuzzy-matching.Rmd

### 2019-02-20 notebook/algae.Rmd
exploring matching on split names

```{r}
length(unmatched2)
head(unmatched2, 10)

ott <- taxa_tbl("ott") %>% collect()
ott_mash <- ott %>% mutate(input = clean_names(scientificName))
```

>>>>

```{r}
length(unmatched2)
head(unmatched2, 10)
```

Working from the names directly:

```{r}
ott <- taxa_tbl("ott") %>% 
  mutate(name1 = splitpart(tolower(scientificName), " ", 1L),
         name2 = splitpart(tolower(scientificName), " ", 2L)
         )
ott
```

```{r}
x <- unmatched2 %>% stringi::stri_extract_all_words(simplify = TRUE) 
colnames(x) <- c("name1", "name2")
x <- as.data.frame(x)
x$sort <- 1:length(x$name1)

sp <-  x %>% filter(name2 != "")
genus_only <- x %>% filter(name2 == "") %>% select(name1, sort)
```

```{r}
match_genus <- right_join(ott, genus_only, copy=TRUE, by = "name1") %>% arrange(sort)
match_genus %>% filter(!is.na(acceptedNameUsageID))
```

```{r}
match_binomial <- right_join(ott, sp, copy=TRUE, by = c("name1", "name2")) %>% arrange(sort)
match_binomial %>% filter(!is.na(acceptedNameUsageID))
```
